A Topic Model of Climate Change Literature

### 2017-09-15 main.tex
Update on Overleaf.

\textbf{
To contribute to evidence-based policies on tackling climate change, the IPCC aims to comprehensively assess the relevant scientific literature \citep{IPCC2013}. With the size of this literature currently almost two orders of magnitude larger than at the time of the IPCC's first assessment report \citep{Houghton1990ClimateAssessment}, this task has become impossible without the aid of machine-reading. We collect over 400,000 abstracts from Web of Science (WoS) and Scopus, and develop a topic model in order to give an overview of this unmanageably large corpus. This overview shows us the distribution and development of topics across the literature, and allows us to identify topics with greater and lesser representation in IPCC reports. %[We find that new topics, such as [biochar] can be identified as they emerge, an application with a high potential for increasing the relevance and comprehensiveness of future IPCC assessments.]
}

@@

@@

\begin{figure}
	\includegraphics[width=\linewidth]{plots/ipcc_topics}
    \caption{IPCC references by topic. The bars show the percentage of each topic that has been matched to an IPCC reference}
    \label{IPCC}
\end{figure}

@@

\section*{Results}
\subsection*{Literature Description}
\begin{itemize}
	\item Some big/interesting topics are x and y
	\item These topics have grown at particularly interesting times (Figure \ref{topic_growth})
    \item These topics are better covered in IPCC, these are less well covered \ref{IPCC}
    \item Some interesting topic correlations are x and y; well fitting documents to both include x and y
    \item
\end{itemize}

@@

\begin{figure}
	\includegraphics[width=\linewidth]{plots/snip}
    \caption{Topic structure of climate change literature [network plot]}
    \label{network}
\end{figure}

>>>>

\textbf{
To contribute to evidence-based policies on tackling climate change, the IPCC aims to comprehensively assess the relevant scientific literature \citep{IPCC2013}. With the size of this literature currently almost two orders of magnitude larger than at the time of the IPCC's first assessment report, this task has become impossible without the aid of machine-reading. We collect over 400,000 abstracts from Web of Science (WoS) and Scopus, and develop a topic model in order to give an overview of this unmanageably large corpus. This overview shows us the distribution and development of topics across the literature, and allows us to identify topics with greater and lesser representation in IPCC reports. %[We find that new topics, such as [biochar] can be identified as they emerge, an application with a high potential for increasing the relevance and comprehensiveness of future IPCC assessments.]
}

@@

\section*{Results}

\todo{From here on in, the paper is more of an outline, with a mixture of bullet points about results that exist or I would still like to generate}

\begin{figure}
\begin{center}
	\includegraphics[width=0.8\linewidth]{plots/network_wg_65}
    \caption{Topic structure of climate change literature}
    \label{network}
    \end{center}
\end{figure}

\subsection*{Topic Model}
\begin{itemize}
	\item Figure \ref{network} shows the structure of the topic model with 100 topics, with each node coloured according to the IPCC working group in which the highest proportion of the topic's documents are cited.
    \item Topics that systematically co-occur in documents are linked, and the resulting network is displayed with links weighted according to topic correlation score. The strength of links is greater where two topics are categorised as 
\end{itemize}

@@

\begin{figure}
	\includegraphics[width=\linewidth]{plots/ipcc_topics_65}
    \caption{IPCC references by topic. The bars show the percentage of each topic that has been matched to an IPCC reference}
    \label{IPCC}
\end{figure}

@@

\subsection*{Literature Description}
\begin{itemize}
	\item Some big/interesting topics are x and y
	\item These topics have grown at particularly interesting times (Figure \ref{topic_growth})
    \item These topics are better covered in IPCC, these are less well covered \ref{IPCC}
    \item Some interesting topic correlations are x and y; well fitting documents to both include x and y
    \item
\end{itemize}

@@
